Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-08 draft.tex
fix proof of prop 2 for alpha and nu positive

Multiplying Condition 3 by $-(1-p_{1s})$, we have $-\beta \cdot (1-p_{1s}) \geq -\alpha \cdot (1-p_{1s})$. Using this with Condition 4, we have $\nu p_{1s} - \beta (1-p_{1s}) \geq \lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta> 0 \ \forall p_{1s},p_{2s}$ and therefore also
\[
  \textstyle -\left(\frac{-\nu p_{1s} + \beta (1-p_{1s})}{1 -\de}\right) \geq \frac{\lambda p_{1s} - \alpha (1-p_{1s})+ \mu + \beta}{1 - \de}> 0 \ \forall p_{1s},p_{2s}
\]

@@

Player $p$'s continuation value when the status quo is played for $m-1$ periods before ceding is $0 + \frac{\de^m}{1-\de} \alpha$, whereas the continuation value from war is $\frac{\lambda p_{1s} + \alpha (1-p_{1s})}{1-\de}$. For player $c$, it is $0 + \frac{\de^m}{1-\de} \beta$ versus $\frac{\nu p_{1s} + \beta p_{2s}}{1-\de}$. Thus the condition for $p$'s willingness to instigate fighting to outweigh $c$'s willingness to deter fighting is
\[
  \textstyle \frac{\lambda p_{1s} + \alpha (1-p_{1s})}{1-\de} - \frac{\de^m}{1-\de} \alpha > \frac{\nu p_{1s} + \beta (1-p_{1s})}{1-\de} - \beta \frac{\de^m}{1-\de} \alpha
\]

>>>>

Multiplying Condition 3 by $-(1-p_{1s})$, we have $-\beta \cdot (1-p_{1s}) \geq -\alpha \cdot (1-p_{1s})$. Using this with Condition 4, we have $\nu p_{1s} - \beta (1-p_{1s}) \geq \lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta> 0 \ \forall p_{1s}$ and therefore also
\[
  \textstyle -\left(\frac{-\nu p_{1s} + \beta (1-p_{1s})}{1 -\de}\right) \geq \frac{\lambda p_{1s} - \alpha (1-p_{1s})+ \mu + \beta}{1 - \de}> 0 \ \forall p_{1s}
\]

@@

Player $p$'s continuation value when the status quo is played for $m-1$ periods before ceding is $0 - \frac{\de^m}{1-\de} \alpha$, whereas the continuation value from war is $\frac{\lambda p_{1s} - \alpha (1-p_{1s})}{1-\de}$. For player $c$, it is $0 + \frac{\de^m}{1-\de} \beta$ versus $\frac{-\nu p_{1s} + \beta (1 - p_{1s})}{1-\de}$. Thus the condition for $p$'s willingness to instigate fighting to outweigh $c$'s willingness to deter fighting is
\[
  \textstyle \frac{\lambda p_{1s} - \alpha (1-p_{1s})}{1-\de} + \frac{\de^m}{1-\de} \alpha > \frac{-\nu p_{1s} + \beta (1-p_{1s})}{1-\de} -  \frac{\de^m}{1-\de} \beta
\]
